Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd

Extensive diagnostics were performed to assess model convergence, fit, and predictive performance. Graphs and more details can be found in the relevant appendices. We evaluated model convergence using the R-hat statistic and trace plots. Trace plots, @sec-trace-plots show well-mixed chains without discernible trends, further supporting the reliability of the MCMC sampling process.

Posterior predictive checks were conducted to assess the model's ability to replicate observed data, @sec-ppc. Density overlay plots for both Trump and Harris models indicated reasonable fits, although some discrepancies were noted near the peaks of the distributions. Specifically, the Trump model's replicated data tended to be slightly smaller around the peak, while the Harris model exhibited more extreme differences at the peak.

@@

## Trace Plots {#sec-trace-plots}

```{r}
#| fig-cap: Trump Trace Plots
#| echo: false
#| warning: false
#| message: false

plot_path <- here::here("other", "plots","trump_trace.pdf" )
knitr::include_graphics(plot_path)

```{r}
#| fig-cap: Harris Trace Plots
#| echo: false
#| warning: false
#| message: false

plot_path <- here::here("other", "plots","harris_trace.pdf" )
knitr::include_graphics(plot_path)

>>>>

Diagnostics were performed to assess model convergence, fit, and predictive performance. Graphs and more details can be found in the relevant appendices. Posterior predictive checks were conducted to assess the model's ability to replicate observed data, @sec-ppc. Density overlay plots for both Trump and Harris models indicated reasonable fits, although some discrepancies were noted near the peaks of the distributions. Specifically, the Trump model's replicated data tended to be slightly smaller around the peak, while the Harris model exhibited more extreme differences at the peak.

@@
